---
title: "Data Import"
output: github_document
---

```{r setup}
library(tidyverse)
library(readxl)
library(haven)
```

## Read in some data

Read in the litters dataset.

```{r}
getwd() # current directory
litters_df = read_csv("./data/FAS_litters.csv")
names(litters_df)
litters_df = janitor::clean_names(litters_df)
names(litters_df)
```

## Take a look at the data
```{r}
litters_df # print out the dataset in the console
skimr::skim(litters_df) #data summary
tail(litters_df) #gives last segment of the data
```
use view(litter_df) in the console to take a look at the full dataset

## Options to read_csv

litters_df = read_csv("./data/FAS_litters.csv", skip = 10)
    skip 10 rows, but if print to console, values become variable names
litters_df = read_csv("./data/FAS_litters.csv", skip = 10, col_names = FALSE)
    no column names anymore, made X1, X2... as column names
litters_df = read_csv("./data/FAS_litters.csv", na = c(".", "NA", ""))
    treat those as missing
check out `?read_csv()`for more information

## Other file formats

Read in an Excel file

```{r}
mlb_df = read_excel("./data/mlb11.xlsx", range = "A1:F7")
```
do Veiw(mlb_df) in the console to view the whole data set

Read in SAS file

```{r}
pulse_df = read_sas("./data/public_pulse_data.sas7bdat")
```






